---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pockethostr

<!-- badges: start -->
<!-- badges: end -->

**WORK in PROGRESS** and subject to change.

This is a very early attempt to wrap the EUROCONTROL Data API from [PoketHost][ph] in R.

It will probably result in a more low-level generic package to support [PocketBase][pb]/PocketHost
and a package specific for the EUROCONTROL Data App.

[ph]: <https://pockethost.io/> "PocketHost - Amazingly Simple PocketBase Hosting"
[pb]: <https://pocketbase.io/> "PocketBase - Open Source backend for your next SaaS and Mobile app
in 1 file"

## Installation

You can install the development version of `pockethostr` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pkg_install("euctrl-pru/pockethostr")
```

## Example

List all records in the EUROCONTROL Data app:

```{r list-all-records, eval=FALSE}
library(pockethostr)

app <- "eurocontrol-data-test"
collection <- "nw_traffic"

ph_list_records(
  app = "eurocontrol-data-test",
  api = "/api/collections/",
  collection = "nw_traffic",
  sort = "-FLIGHT_DATE")
```

# Development

In order to build the relevant pkgdown web pages, execute the following code:

```{r pkgdown-cuild, eval=FALSE}
# How to build the pakgdown from behind proxied Internet
library(withr)
library(pkgdown)

with_options(list(pkgdown.internet = FALSE),
             build_site())
```

