---
title: "Create, read, update and delete records"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Create, read, update and delete records}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval=FALSE}
library(pockethostr)

app <- "eurocontrol-data"
collection <- "nw_traffic"
```

## Read records

This is what the mobile app would typically need:
* single record: `perPage = 1`.
* latest temporal entry (descending sort on `FLIGHT_DATE`, `sort = "-FLIGHT_DATE"` ).

Here we also make sure not to ask for totals because this improves performance/speed
on the server side,i.e. set `skipTotal` to any value.

```{r read-record, eval=FALSE}
# only last temporal entry, no totals
ph_list_records(
    app = app,
    api = "/api/collections/",
    collection = collection,
    perPage = 1,
    sort = "-FLIGHT_DATE",
    skipTotal = 1)
```


All (paged) records (two per page, just as an example) and totals.

```{r paged-records, eval=FALSE}
# only one entry, w/ totals
ph_list_records(
  app = app,
  api = "/api/collections/",
  collection = collection,
  perPage = 2,
  sort = "-FLIGHT_DATE")
```


## Authentication

```{r authehticate-admin, eval=FALSE}
username <- "you@colossal-cave.adventure"
password <- "xyzzy"


# req_dry_run(redact_headers = FALSE)
adm <- ph_authenticate_admin_username_password(
    app,
    "/api/admins/auth-with-password",
    username,
    password)
```


## Delete record
You need to know the record ID in order to send a delete request.
You can get all record IDs with a read records request `ph_list_records()`, see above.

You need to pass an admin token to do so (in this app at least), so you need to be authenticated first.

```{r delete-record, eval=FALSE}
ph_delete_record(
  app = app,
  api = "/api/collections/",
  collection = collection,
  id = "pu0kfs31ngg5ec3",
  token = adm$token
)
```


## Create record

```{r create-record, eval=FALSE}
bd <- list(
  DAY_TFC= 24944,
  FLIGHT_DATE= "2024-01-03 00:00:00.000Z",
  Y2D_TFC_YEAR= 440276
)

ph_create_record(
  app = app,
  api = "/api/collections",
  collection = collection,
  token = adm$token,
  body = bd)
```

